\section{ICMP}
\subsection{ICMP types and codes}
\begin{enumerate}[label=\textbf{\alph*.}]
    \item The router sends an ICMP Time Exceeded packet to
    with \texttt{type=11} and \texttt{code=0} which means it is due to TTL running out.
    \item The router sends an ICMP Destination Unreachable packet,
    with \texttt{type=3} and \texttt{code=4} which means that fragmantation was required
    but not allowed due to the DF flag.
    \item The router sends an ICMP Destination Unreachable packet,
    with \texttt{type=3} and \texttt{code=1} which means the destination network is unreachable.
    \item The router sends an ICMP Destination Unreachable packet,
    with \texttt{type=3} and \texttt{code=3} which means
    the destination port is unreachable.
    \item It will send a packet with \texttt{type=5} and \texttt{code=0}
    which indicates that a packet was forwareded but the existing routing is used was not optimal in
    the sense that it should have been routed through the same LAN.
    \item The router will return an ICMP echo reply packet
    which has \texttt{type=0}, \texttt{code=0}.
    \item The router sends an ICMP Destination Unreachable packet,
    with \texttt{type=3} and \texttt{code=0} which
    means that the destination address could not be reached.
\end{enumerate}
\subsection{MTU discovery}
MTU is the Maximum Transmission Unit,
which is a number (in bytes) that describes the maximal size of a packet
that will be sent.\\
MTU discovery is a process where on a specific socket - the two communicating
parties attempt to find the MTU for the links that connect them - so
they can send packets with the optimal size in their communication.\\

MTU discovery is done by attempting different message sizes (and \texttt{DF=1}) and seeing which
are capable of passing and which do not return or result with an 'ICMP could not Fragment' - which
means the packet was too large.
A failiure indicates the packet size is larger than the MTU while 
a success indicates the packet size is smaller or equal to the MTU.
To accelerate this process a binary search algorithm can be used.

\subsection{ICMP and IP}
ICMP is the Internet Control Message Protocol while IP is Internet Protocol.\\
The ICMP protocol enables the IP protocol to work, by transfering
metadata about how IP messages are moving through the network (such as in the examples in the first
part of the question).\\
It is also somewhat circular as ICMP packets are built upon the IP headers,
while the routers and hosts that transfer IP packets relay on the ICMP
protocol to be configured properly.